---
title: "Eleni Partakki"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    df_print: kable
---
<p>&nbsp;</p>

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# Set R chunk default options:
# -do not output all R messages in html report
# -do not output all R warnings in html report
# -set default figure widths and heights for all code blocks, unless you 
#  override them
knitr::opts_chunk$set(
  message = FALSE, warning = FALSE, fig.width = 16/2, fig.height = 9/2
)
```


```{r, echo = FALSE}
#loading libraries

library(ggplot2)
library(lubridate)
library(tidyr)
library(readr)
library(mapview)
library(tidyverse)
library(sf)
library(htmltools)
library(geojsonio)
library(leaflet)
library(USAboundaries)
library(maps)
library(editData)
library(sp)
library(tmaptools)
library(raster)
library(dplyr)
library(mapview)
library(readr)
```

# **About Me**
<p>&nbsp;</p>

Hey there stranger! I am a young engineer with a passion for using technology to solve real-world problems.

I grew up fascinated by the power of machines and how they can be used to make our lives easier. This led me to pursue a degree in engineering, where I gained a deep understanding of the principles that govern the design and operation of mechanical, electrical, and software systems.

Since graduating, I have been fortunate enough to work on a variety of exciting projects that have allowed me to apply my skills and knowledge in a practical setting. Whether it's designing new products, optimizing manufacturing processes, or developing software applications, I am always looking for ways to use my expertise to make a positive impact.

One of the things that I love most about engineering is the way it challenges me to think creatively and analytically. Every problem is unique, and finding a solution often requires a combination of technical know-how, critical thinking, and collaboration with others. This keeps me engaged and motivated, and I am always eager to tackle new challenges.

When I'm not working, you can usually find me tinkering with gadgets and electronics, reading up on the latest industry trends and technologies, or exploring the great outdoors. I believe that a well-rounded life is key to achieving success and happiness, and I try to balance my work and personal interests accordingly.

Thank you for taking the time to read a bit about me. If you'd like to learn more or discuss potential opportunities to collaborate, please don't hesitate to get in touch!
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

## Interests

## Leadership

## Extracurricullar

## Learning

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>


# Software Engineering

# Data Science

# Sales Engineering










